Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.2]

### 2017-02-23 QPQ9/qpq9_draft.tex
Added tables. Draft version 1.2

\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.1]}

@@

\begin{abstract}
Blah
\end{abstract}

@@

\section{Introduction}

%\begin{itemize}
%\item Flows
%\item Mass (Kaiser, Schaye)
%\item Directionality/symmetry
%\item Break the symmetry
%\end{itemize}

%Take words from my summary of SomervilleDave15.

The formation and evolution of stars are dictated
by the flow of gas and metals/dust.  [This transport
varies directly with the stellar stage
and a lesser extent stellar mass.]
The accretion onto a protostellar  core eventually
initiates nuclear fusion.  The main sequence is characterized
by gentler stellar winds, with the most massive
stars shedding a cumulative mass of XX\%.
Stellar deaths, meanwhile, are frequently accompanied by terrific
mass loss, occasionally punctuated by a highly energetic,
supernova phase.

By analogy, galaxy formation and evolution are driven by the
flows into/out of their interstellar medium.
In contrast to most stars, however, current theories
predict (even demand) that the star-forming galaxies
maintin these flows. [add]

Akin to stars, direct observations of galactic flows are
difficult to acquire.  Even detecting the gas is challenging:
the gas mass is either too small or the gas density too low
for the [detection] of line-emission (e.g. 21cm, lya,
or H$\alpha$ from Hydrogen).  Resolving the kinematics
and establish the mass-flux represent a far greater challenge.
These challenges are accentuated for distant, young galaxies
where flows are predicted to prevail \citep{keres,fumagalli}.
Therefore, with rare exceptions \citep[e.g.][]{slug,jackpot},
the community has relied on absorption-line spectroscopy
to detect and characterize the gas surrounding galaxies
\citep[e.g.][]{bergeron,steidel10,pro11,tumlinson13}.
With this experiment, researcher have had recent success
in characterizing the large-scale flows around star-forming
galaxies to reveal a net inflow \cite{rakic13} and
provide unique constraints on the mass of the underlying
potential well \cite{rakic14}.

A significant limitation of standard absorption-line
analysis, especially regarding sutyding galactic flows,
is the inherent symmetry of the experiment.
Because one generally lacks any constraint on the distance
of the gas along the sightline,
postive or negative velocities with respect to the
galaxy may be interpreted as gas flowing either towards
or away from the system.
So-called `down-the-barrel' observations break this
symmetry, and have generally provided evidence for flows
away from galaxies \citep{rupke,martin,weiner,rubin}.
However, these data are frequently at low spectral resolution
which limits one's sensitivity to inflowing gas.

In this paper, we examine the flows of gas in the environments
of massive galaxies hosting quasars.  Our approach leverages
a large dataset of quasar pairs \citep{hennawi}
to use the standard technique of absorption-line spectroscopy
with background quasars. [word]
These quasar pairs have angular
separations that correspond to less than 300\,kpc physical
separation at the f/g quasar redshift.
Our previous publications from these quasar pairs
have established that these galaxies are surrounded
by a massive, cool, and enriched circumgalactic medium
\citep{QPQ1,QPQ5,QPQ6,QPQ7}.
We have collected a sample of ntot~spectra passing within
300\,kpc from a f/g quasar with a precisely measured
redshift.  Our primary scientific interests are twofold:
(i) search for signatures of galactic-scale outflows from the
central galaxy, presumably driven by recent star-formation
and/or AGN feedback;
(ii) characterize the dynamics of galactic flows around these
massive system.  We further descrbie an aspect of this
experiment that offers a unique opportunity to study galactic
flows. [detail??]

Throughout this manuscript we adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda
=0.74$, and $H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. All distances are proper unless otherwise 
stated. 
%When referring to comoving distances we include explicitly an $h^{-1}$ term and 
%follow modern convention of scaling to a Hubble constant of $70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. All 
%equivalent width measurements are presented in the rest-frame, unless otherwise specified.

\section{The Experiment}
\label{sec:data}

From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed 195~systems 
that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict the sample 
to foreground quasars with redshift measured from \ion{Mg}{2}, [\ion{O}{3}], H$\alpha$, or 
H$\beta$ emission, giving a precision of $400\,{\rm km\,s^{-1}}$ or lower. [\ion{O}{3}] has the 
smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the 
sub-sample with [\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift 
of $27\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 we have 
quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
\citep{hewittwild}.
We include only those spectra with S/N~$> XX$\AA\ at the
observed wavelengths of lya, \ion{C}{2}~1334, or 
\ion{C}{4}~1548 transitions.  Of the ntot~sightlines, 
nhigh\ have spectral resolution ~$> 5,000$ from echellette
or echelle observations (QPQ8).  This high-dispersion 
sample is analyzed [separately] throughout the paper.
Figure~\ref{fig:exp} summarizes the experimental design.
Refer to previous QPQ
publications for details on data reduction
and continuum normalzaton (QPQ6, QPQ7, QPQ8).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
\label{sec:analysis}

In QPQ8, we measured the velocity widths of the \ion{C}{2}~1334
and \ion{C}{4}~1548 transitions finding that the CGM
frequently exhibits large flows:
median DV{1334},DV{1548} = $XX,XX kms$ with and
RMS DRMS{1334},DRMS{1548} = $XX, XX kms$ from
a sample of ncii\ and nciv\ systems.
These velocity fields exceed all previous measurements from
galaxies and/or absorption systems at any epoch.  For
Figure~\ref{fig:stack}, we present these absorption lines
and \ion{H}{1}~lya, also including lower-dispersion 
sightlines meeting the selection criteria.

To assess the `average' absorption of these transitions,
we have combined the data with a novel technique.
We have fitted the combined dataset using a cubic b-spline
with knots at every 100\,kms.  We weighted each data
point by the velocity width of the pixel to insure that 
each sightline makes an equal contribution to the stack.
These b-spline profiles are presented in the figure
and a trivial integration gives the reported equivalent
widths.
[consider down-weighting systems with $<3\sigma$ EW]
[Comnent on EW from 'standard' technique]

Two results are evident from the figure:
 (i) the data exhibit excess absorptoin at 
 $mdv \approx 0 kms$;
 (ii) the absorption is skewed towards positive velocities
 $mdv > 0 mkms$.
We measure absorption-weigthed ($1-f$) centroids
of $mdv = XX-XX mkms$ for these transitions
(Table~\ref{tab:summ}).
This suggests an asymmetry that contradicts the [standard]
expectation.

Given the small sample size, one must 
scrutinize the statistical significance of the measured offset.
Indeed, a small offset $mdv < 10 kms$ may be expected
even with large samples.  To assess the statistical significance,
we have perfomed a boostrap analysis by randomly resampling
from the full sample. [DISCUSS]

[Discuss systematics here??]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}

[Add a cartoon fig with cone]
[Is it really obvious that this works??]

%%%%%%%%%%%%%%%%
\acknowledgements

JXP and ML acknowledge support from the National
Science Foundation (NSF) grant AST-1010004 and AST-XX. 
JXP thanks the Alexander
von Humboldt foundation for a visitor fellowship to the MPIA where
part of this work was performed, as well as the staff at MPIA for
their hospitality during his visits.
JFH acknowledges generous support from the Alexander von Humboldt
foundation in the context of the Sofja Kovalevskaja Award. The
Humboldt foundation is funded by the German Federal Ministry for
Education and Research.

%Much of the data presented herein were obtained at the W.M. Keck
%Observatory, which is operated as a scientific partnership among the
%California Institute of Technology, the University of California, and
%the National Aeronautics and Space Administration. The Observatory was
%made possible by the generous financial support of the W.M. Keck
%Foundation.  Some of the Keck data were obtained through the NSF
%Telescope System Instrumentation Program (TSIP), supported by AURA
%through the NSF under AURA Cooperative Agreement AST 01-32798 as
%amended.
%
%Some of the data herein were obtained at the Gemini Observatory, which
%is operated by the Association of Universities for Research in
%%Astronomy, Inc., under a cooperative agreement with the NSF on behalf
%of the Gemini partnership: the NSF (United
%States), the Science and Technology Facilities Council (United
%Kingdom), the National Research Council (Canada), CONICYT (Chile), the
%Australian Research Council (Australia), Minist\'{e}rio da
%Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil) and Ministerio de
%Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina). 
%
%The authors wish to recognize and acknowledge the very
%significant cultural role and reverence that the summit of Mauna Kea
%has always had within the indigenous Hawaiian community. We are most
%fortunate to have the opportunity to conduct observations from this
%mountain.
%Acknowledge TK Chan. CP Choi.

\bibliographystyle{/u/xavier/paper/Bibli/apj}
\bibliography{/u/xavier/paper/Bibli/allrefs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{../Tables/tab_sub_qpq7_spectra.tex}
\input{Tables/tab_summ.tex}
%\input{Tables/tab_summ_Hab.tex}
%\input{tab1_sub.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\begin{figure}
\includegraphics[width=5in]{Figures/fig_experiment.pdf}
%\includegraphics[width=5in,angle=90]{../Figuref1.eps}
\caption{Experimental design
}
\label{fig:exp}
\end{figure}

\begin{figure}
%\includegraphics[width=5in]{Figures/fig_simple_stack.pdf}
%\includegraphics[width=5in,angle=90]{f2.eps}
\caption{Simple stack
}
\label{fig:stack}
\end{figure}

>>>>

\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.2]}

@@

\begin{abstract}
Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
environments of massive galaxies hosting quasars at $z\sim2$. We employ 195 projected quasar pairs 
to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large intrinsic velocity fields, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue the results can be 
explained by outflowing gas combined with anisotropic or intermittent ionizing radiation of the 
quasars. 
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
%\begin{itemize}
%\item Flows
%\item Mass (Kaiser, Schaye)
%\item Directionality/symmetry
%\item Break the symmetry
%\end{itemize}

Galaxy formation and evolution are driven by the flows into and out of their interstellar medium. 
Current theories demand that star-forming galaxies maintain these flows. Gas accretes, cools, and 
adds to the fuel supply, while star formation feedback heats gas, blows it out of galaxies, and 
regulates star formation \citep[for a review see][]{SomervilleDave15}.

Direction observations of galactic flows are difficult to acquire. Detecting the presence of 
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for 
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving 
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are 
accentuated for distant, young galaxies, where flows are predicted to prevail 
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions, 
\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy 
to detect and characterize the gas surrounding galaxies 
\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}. With this 
experiment, researchers have had success in characterizing the large-scale flows around 
star-forming galaxies to reveal a net inflow, or a Kaiser effect for gas \citep{Rakic+12}.

A significant limitation of absorption-line analysis, especially regarding galactic flows, 
is the inherent symmetry of the experiment. One generally lacks any constraint on the distance of 
the gas along the sightline. Positive or negative velocities with respect to the galaxy may be 
interpreted as gas flowing either toward or away from the system. ``Down-the-barrel'' observations 
break this symmetry, and have generally provided evidence for flows away from galaxies 
\citep{Rupke+05,Martin05,Weiner+09,Rubin+14}. However, these data are frequently at low spectral 
resolution which limits one's sensitivity to inflowing gas.

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][QPQ1]{QPQ1} to use the 
standard technique of absorption-line spectroscopy with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched circumgalactic medium 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 195 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Our primary 
scientific interests are twofold: (i) search for signatures of galactic-scale outflows from the 
central galaxy, presumably driven by recent star formation and/or active galactic nuclei feedback; 
(ii) characterize the dynamics of galactic flows around these massive system. We further describe 
an aspect of this experiment that offers a unique opportunity to study galactic flows: we argue 
that, the anisotropic or intermittent radiation of the foreground quasars breaks the symmetry in 
the velocity field of circumgalactic absorbers.

Among the sightlines in the QPQ9 sample, 13 have spectral resolution $> 5000$ from echellette or 
echelle observations, and have been analyzed separately in QPQ8 \citep{QPQ8}. We measured the 
velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the CGM frequently exhibits 
large flows that are offset from the systemic redshift. The offsets, $\delta v$, are often 
positive, with the sign convention that positive velocities are flowing away from the observer. 
From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4} systems, we measured the velocity 
interval that encompasses 90\% of the total optical depth, $\Delta v_{90}$, and the $1\sigma$ 
dispersion relative to the profile centroid, $\sigma_v$. The median $\Delta v_{90}$ is 
$555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is $342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. 
The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is 
$495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed all previous 
measurements from galaxies and/or absorption systems at any epoch.

%The formation and evolution of stars are dictated
%by the flow of gas and metals/dust.  [This transport
%varies directly with the stellar stage
%and a lesser extent stellar mass.]
%The accretion onto a protostellar  core eventually
%initiates nuclear fusion.  The main sequence is characterized
%by gentler stellar winds, with the most massive
%stars shedding a cumulative mass of XX\%.
%Stellar deaths, meanwhile, are frequently accompanied by terrific
%mass loss, occasionally punctuated by a highly energetic,
%supernova phase.
%By analogy, galaxy formation and evolution are driven by the
%flows into/out of their interstellar medium.
%In contrast to most stars, however, current theories
%predict (even demand) that the star-forming galaxies
%maintin these flows. [add]
%Akin to stars, direct observations of galactic flows are
%difficult to acquire. Even detecting the gas is challenging:
%the gas mass is either too small or the gas density too low
%for the [detection] of line-emission (e.g. 21cm, lya,
%or H$\alpha$ from Hydrogen).  Resolving the kinematics
%and establish the mass-flux represent a far greater challenge.
%These challenges are accentuated for distant, young galaxies
%where flows are predicted to prevail \citep{keres,fumagalli}.
%Therefore, with rare exceptions \citep[e.g.][]{slug,jackpot},
%the community has relied on absorption-line spectroscopy
%to detect and characterize the gas surrounding galaxies
%\citep[e.g.][]{bergeron,steidel10,pro11,tumlinson13}.
%With this experiment, researcher have had recent success
%in characterizing the large-scale flows around star-forming
%galaxies to reveal a net inflow \cite{rakic13} and
%provide unique constraints on the mass of the underlying
%potential well \cite{rakic14}.
%A significant limitation of standard absorption-line
%analysis, especially regarding sutyding galactic flows,
%is the inherent symmetry of the experiment.
%Because one generally lacks any constraint on the distance
%of the gas along the sightline,
%postive or negative velocities with respect to the
%galaxy may be interpreted as gas flowing either towards
%or away from the system.
%So-called `down-the-barrel' observations break this
%symmetry, and have generally provided evidence for flows
%away from galaxies \citep{rupke,martin,weiner,rubin}.
%However, these data are frequently at low spectral resolution
%which limits one's sensitivity to inflowing gas.
%In this paper, we examine the flows of gas in the environments
%of massive galaxies hosting quasars.  Our approach leverages
%a large dataset of quasar pairs \citep{hennawi}
%to use the standard technique of absorption-line spectroscopy
%with background quasars. [word]
%These quasar pairs have angular
%separations that correspond to less than 300\,kpc physical
%separation at the f/g quasar redshift.
%Our previous publications from these quasar pairs
%have established that these galaxies are surrounded
%by a massive, cool, and enriched circumgalactic medium
%\citep{QPQ1,QPQ5,QPQ6,QPQ7}.
%We have collected a sample of ntot~spectra passing within
%300\,kpc from a f/g quasar with a precisely measured
%redshift.  Our primary scientific interests are twofold:
%(i) search for signatures of galactic-scale outflows from the
%central galaxy, presumably driven by recent star-formation
%and/or AGN feedback;
%(ii) characterize the dynamics of galactic flows around these
%massive system.  We further descrbie an aspect of this
%experiment that offers a unique opportunity to study galactic
%flows. [detail??]

We adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda=0.74$, and 
$H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. Distances are proper unless otherwise stated. When referring 
to comoving distances we include explicitly an $h^{-1}$ term and follow modern convention of 
scaling to a Hubble constant of $70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. 
%All equivalent width measurements are presented in the rest-frame, unless otherwise specified.

\section{The Experiment}
\label{sec:experiment}

\begin{figure}
\includegraphics[width=3in]{Figures/fig_experiment.pdf}
\caption{These panels summarize properties of the QPQ9 dataset. The QPQ survey selects 
quasar pairs of $R_\perp < 300$\,kpc and $z_{\rm fg}>1.6$. Assuming that the foreground quasars 
emit isotropically and at a distance equal to the impact parameter, the aenhancement in the UV 
flux relative to the extragalactic UV background, $g_{\rm UV}$, can be estimated. Large 
symbols correspond to foreground quasars with the most precise redshift measurement from 
[\ion{O}{3}]\,5007, while small symbols correspond to $z_{\rm fg}$ 
measurements from \ion{Mg}{2}\,2800, H$\alpha$, or H$\beta$ emission. The top panel shows 
quasar pairs with coverage of \ion{C}{2}\,1334 at $z_{\rm fg}$ in the background quasar spectra. 
The middle panel shows pairs with coverage of \ion{C}{4}\,1548. The bottom panel shows 
pairs with coverage of \ion{Mg}{2}\,2796. 
}
\label{fig:experiment}
\end{figure}

The goal of our experiment is to measure the average velocity fields of the absorption from C$^+$, 
C$^{3+}$, and Mg$^+$ ions associated with the CGM of the massive galaxies hosting $z\sim 2$ 
quasars.

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we have analyzed a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
$400\,{\rm km\,s^{-1}}$ or better. 
[\ion{O}{3}] emission-line redshifts have the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about 
the systemic redshift, and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
redshift \citep{Boroson05}, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 
\citep{QPQ8}, we have quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. We further add to the QPQ 
dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
Twelfth Data Release \citep{Paris+17}. We 
only select pairs with $z_{\rm fg}$ measured by \cite{HewettWild10} using the \ion{Mg}{2}\,1800 
emission-line. We reached a final sample size of 195. Figure~\ref{fig:experiment} summarizes the 
experimental design. We refer the reader to previous QPQ publications for the details on the 
redshift centroiding algorithm, data reduction, and continuum normalization (QPQ6; QPQ8).

As in the previous QPQ papers, we select the quasar pairs to have redshift difference 
$>3000\,{\rm km\,s^{-1}}$, to exclude physically associated binary quasars. The cut on velocity 
difference is motivated by the typical redshift uncertainty of $\approx500\,{\rm km\,s^{-1}}$ of 
the background quasars. In QPQ8, it was required that the observed wavelengths of the 
metal ion transitions fall outside the Ly$\alpha$ forest of the background quasar. In this paper, 
we exclude a small window around the Ly$\alpha$ emission, in additional to the Ly$\alpha$ forest, 
from analysis. For stacked profile analysis, a good estimate of 
the continuum level is neessary. In QPQ8 we found that absorption associated to 
the foreground quasar occurs within $\pm2000\,{\rm km\,s^{-1}}$ around $z_{\rm fg}$. Therefore, it 
is desirable to keep a $\approx\pm3000\,{\rm km\,s^{-1}}$ window relatively free of contamination 
from Ly$\alpha$ forest. Taking into account the redshift uncertainties, 
we decide that at least one transition among \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 at $z_{\rm fg}$ must lie redward of 
$(1215.6701+20)\times(1+z_{\rm bg})\,{\rm \AA}$, for a pair to be included in the analysis.

Furthermore, we include only those spectra with average signal-to-noise ratio (S/N) exceeding 5.5 
per rest-frame \AA \ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths 
of the metal ion transitions. This criterion is a compromise between maximizing sample size versus 
maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame 
\AA \ is 
necessary for properly estimating the continuum, as well as identifying mini-broad absorption line 
systems associated to the background quasar, which will significantly depress the flux level. We 
also require that the region of the spectrum that is $\pm3000\,{\rm km\,s^{-1}}$ around a 
considered metal ion transition does not overlap with strong atmospheric ${\rm O}_2$ bands. 
The ${\rm O}_2$ A- and B-band span 7595\textendash7680\,\AA \ and 6868\textendash6926\,\AA \ 
respectively.

Table~\ref{tab:sample} lists the full QPQ9 sample. 
In Table~\ref{tab:summary}, we list the sample size, the median $z_{\rm fg}$, and the median 
$R_\perp$ of the quasar pairs that survive the above selection criteria for \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively. In Table~\ref{tab:summary_OIII}, we provide 
the summary for the sub-sample with $z_{\rm fg}$ measured from [\ion{O}{3}].

\input{Tables/tab_sample.tex}
\input{Tables/tab_summ.tex}
\input{Tables/tab_summ_OIII.tex}

\section{Analysis}
\label{sec:analysis}

\begin{figure}
\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thick, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thin, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$.  
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unncessary to smooth the data to a 
common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than error sources. The mean statistic of the individual spectra yields a good estimate of the 
average absorption and preserves equivalent width. The median statistic is less sensitive to 
outliers, however the averaged equivalent width is smaller and the analysis on the velocity field 
becomes more uncertain. In the following we present stacked spectra using both the mean and the 
median statistic.

[Update the mean and scatter of emission-line redshifts relative to systemic to Shen+16?]

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to interpret their kinematics, while the median stacks have smaller 
equivalent widths.

%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]

Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is skewed 
toward positive velocities. To model the absorption, we introduce a Gaussian profile while 
allowing a constant pseudo-continuum level to vary. From the $\chi^2$ best-fit to the data, 
we measure the centroid of the \ion{C}{2} stack to be $+170\,{\rm km\,s^{-1}}$ and 
the $1\sigma$ dispersion to be $388\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The 
median stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid 
closer to zero.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
$+207\,{\rm km\,s^{-1}}$, and a dispersion of $355\,{\rm km\,s^{-1}}$, consistent with the full 
sample.

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a  
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. The 
modeling results show that the velocity fields of \ion{C}{4} and \ion{Mg}{2} are consistent with 
\ion{C}{2}, i.e.\ large dispersion and centroid is skewed toward positive velocities.

The above analyses are summarized in Table~\ref{tab:summary} and Table~\ref{tab:summary_OIII}. The 
Gaussian models normalized to pseudo-continuum are overplotted on the data stacks in 
Figure~\ref{fig:stacks_and_fits}.

\subsection{Significance of the asymmetric absorption}
\label{sec:significance_+ve}

\begin{figure*}[!h]
\begin{minipage}[!bp]{0.35\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\end{minipage}%
\hspace{0.5in}
\begin{minipage}[!bp]{0.55\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
absorbers at all distances, shows a large, blueshifted mean velocity field.
}
\label{fig:stacks_fg}
\end{minipage}
\end{figure*}

Given the small sample size, one must scrutinize the statistical significance of the measured 
velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
randomly sampling from the full sample 10000 times. We measure the flux-weighted centroid of each 
bootstrap realization, and quote the standard deviation in the bootstrap realizations to be the 
scatter in the centroid of the data. The scatters $\approx100\,{\rm \,s^{-1}}$ are comparable 
to the measured offsets, indicating large intrinsic variation in quasar CGM environments (see 
also QPQ8). Given the large intrinsic scatter, we do not attempt to explore whether there exists 
relative asymmetry between \ion{C}{2} and \ion{C}{4} absorption due to different ionization 
potentials.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a \ion{Mg}{2}, H$\alpha$, or 
H$\beta$ redshift. We are able to replace for 13 out of the 14 systems with [\ion{O}{3}] redshifts 
in the original sample. The new stack is similiar in velocity structure and again shows a positive 
offset. We thus conclude that our algorithm for measuring redshifts is not severely biased by 
the blue wing of the [\ion{O}{3}] emission-line.

We also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs, 
using the same selection criteria as the main QPQ9 sample. The quasar pairs are selected from the 
igmspec database, with $z_{\rm fg}$ measured by \cite{HewettWild10}. There are 231 pairs selected, 
with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present the mean and 
median stacks in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
sample. Gaussian absorption models fitted to the stack recover a centroid of 
$47\pm122\,{\rm km\,s^{-1}}$ and a dispersion of $119\,{\rm km\,s^{-1}}$. The offsets from 
$0\,{\rm km\,s^{-1}}$ are smaller than the offsets in the $z\sim2$ sample.

Since the large scatters in the centroids represent intrinsic variation rather than redshift 
errors, and the \ion{Mg}{2} stack for lower redshift does not suggest a similar offset, the hint 
of asymmetry cannot be ignored. In the Discussion section, we discuss two possible explanations 
for the asymmetry.

%Indeed, a small offset $mdv < 10 kms$ may be expected even with large samples.

\subsection{Significance of the large velocity fields}
\label{sec:significance_width}
